External Patch Group Prior Guided Internal Orthogonal Dictionary Learning for Real Image Denoising

### 2016-10-24 CVPR2017_Review_Unified.tex
ad

%%%%%%%%% ABSTRACT
\begin{abstract}
For image denoising problem, the external and internal priors are playing key roles in many different methdos. External priors learn from external images to restore noisy images while internal ones exploit priors of given images for denoising. The external priors are more generative and efficient on recovering structures existing in most images while the internal priors are more adaptive on recovering detials existed in given noisy images. In this paper, we propose to employ the external patch group prior of images to guide the clustering of internal patch groups, and develop an external dictionary guided internal orthogonal dictionary learning algorithm for real image denoising. The internal orthogonal dictionary learning process has closed-form solutions and hence very efficient for online denoising. The experiments on standard datasets demonstrate that, that the proposed method achieves much better denoising performance than the other state-of-the-art methods on real image denoising. 
\end{abstract}
%Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise. Therefore, only exploiting the external or internal priors are not enough for real image denoising.

@@

In the last decade, the methods of \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} are developed to deal with real noisy images. Almost all these methods employ a two-stage framework: estimating the parameters of the assumed noise model (usually Gaussian) and performing denoising with the help of the noise modeling and estimation in the first stage. However, the Gaussian assumption is inflexible in describing the complex noise on real noisy images \cite{Liu2008}. Although the mixture of Gaussians (MoG) model is possible to approximate any noise distribution \cite{Bishop}, estimating its parameters is time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR}. To evaluate the performanec of these methods on dealing with complex real noise, we apply these methods, with corresponding default parameters, on a real noisy image provided in \cite{crosschannel2016}. The testing image is captured by a Nikon D800 camera when ISO is 3200. The "ground truth" image is also provided with which we can calculate objective measurements such as PSNR and SSIM \cite{ssim}. The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or oversmooth the complex details in real noisy image. 
\begin{figure*}\label{fig1}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) CBM3D \cite{cbm3d} \\ (33.33dB/0.8935)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) MLP \cite{mlp}\\ (34.22dB/0.9603) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) CSF \cite{csf}\\ (35.39dB/0.9677) }
\end{minipage}
}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) TRD \cite{chen2015learning} \\ (35.97dB/0.9705)   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (i) Ours \\ (\textbf{37.28}dB/\textbf{0.9729})  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (j) Mean Image }
\end{minipage}
}
\caption{Denoised images of the real noisy image "$Nikon D800 ISO 3200 A3$" by different methods. The images are better to be zoomed in on screen.}
\end{figure*}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
For image denoising problem, the external and internal priors are playing key roles in many different methdos. External priors learn from external images to restore noisy images while internal ones exploit priors of given images for denoising. The external priors are more generative and efficient on recovering structures existing in most images while the internal priors are more adaptive on recovering detials existed in given noisy images. In this paper, we propose to employ the external patch group prior of images to guide the clustering of internal patch groups, and develop an external dictionary guided internal orthogonal dictionary learning algorithm for real image denoising. The internal orthogonal dictionary learning process has closed-form solutions and hence very efficient for online denoising. The experiments on standard datasets demonstrate that, that the proposed method achieves better performance than other state-of-the-art methods on real image denoising. 
\end{abstract}
%Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise. Therefore, only exploiting the external or internal priors are not enough for real image denoising.

@@

In the last decade, the methods of \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} are developed to deal with real noisy images. Almost all these methods employ a two-stage framework: estimating the parameters of the assumed noise model (usually Gaussian) and performing denoising with the help of the noise modeling and estimation in the first stage. However, the Gaussian assumption is inflexible in describing the complex noise on real noisy images \cite{Liu2008}. Although the mixture of Gaussians (MoG) model is possible to approximate any noise distribution \cite{Bishop}, estimating its parameters is time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR}. To evaluate the performanec of these methods on dealing with complex real noise, we apply these methods, with corresponding default parameters, on a real noisy image provided in \cite{crosschannel2016}. The testing image is captured by a Nikon D800 camera when ISO is 3200. The "ground truth" image is also provided with which we can calculate objective measurements such as PSNR and SSIM \cite{ssim}. The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or oversmooth the complex details in real noisy image. 
\begin{figure*}\label{fig1}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) CBM3D \cite{cbm3d} \\ (33.33dB/0.8935)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) MLP \cite{mlp}\\ (34.22dB/0.9603) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) CSF \cite{csf}\\ (35.39dB/0.9677) }
\end{minipage}
}\vspace{-3mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) TRD \cite{chen2015learning} \\ (35.97dB/0.9705)   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (i) Ours \\ (\textbf{37.28}dB/\textbf{0.9729})  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (j) Mean Image }
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of the real noisy image "Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} \vspace{-4mm}
\end{figure*}
